Homework 4

### 2019-09-26 hw4/MSimonsHW4.tex
number 3 hw 4

\item First, let us prove that $\cong$ is symmetric.
Since $f: R \rightarrow S$ is an isomorphism, this means that $f$ is bijective.
Let $f(r) = s$ for some $r \in R$ and some $s \in S$.
If $f$ is bijective, there exists some function $g: S \rightarrow R$ such that
$g(s) = g(f(r)) = r$. \\ \\
To prove $g$ is injective, let $s, s' \in S$ and $r, r' \in R$ such that
$s \neq s'$, $r \neq r'$, $f(s) = r$, and $f(s') = r'$.  As such,
$g(s) = g(f(r)) = r$ and $g(s') = g(f(r')) = r'$.  Since $r \neq r'$, this
implies that if $s \neq s'$, then $r \neq r'$ and $g$ must be injective. \\ \\
Because Im $f$ = $S$, there is an $r \in R$ for all $s \in S$ such that
$s = f(r)$.  Because $g(s) = g(f(r)) = r$, Im $g$ = $R$ and $g$ is surjective. \\ \\
We can prove that $g(s) + g(s') = g(s + s')$ as such: \\
\[
g(s) + g(s') = g(f(r)) + g(f(r')) = r + r' = g(f(r + r')) = g(f(r) + f(r')) = g(s + s')
\]
\\
We can prove $g(s)g(s') = g(ss')$ as such:
\[
g(s)g(s') = g(f(r))g(f(r')) = rr' = g(f(rr')) = g(f(r)f(r')) = g(ss')
\]
\\
Therefore, $g$ is an isomorphism and $\cong$ is symmetric.
\\ \\
Next, we prove that $\cong$ is transitive.  If $f$ and $g$ are isomorphisms,
then there exists $r \in R$, $s \in S$, and $t \ in T$ such that
$f(r) = s$ and $g(s) = t$.  As such, let $h: R \rightarrow T$ be the function
such that $h(r) = g(f(r)) = g(s) = t$. \\ \\
Let $g(s') = t'$ for some $s' \in S$ and $t' in T$ such that
$s \neq s'$ and $t \neq t'$.
We know $h$ is injective because $h(r) = g(f(r)) = g(s) = t$ and
$h(r') = g(f(r')) = g(s') = t'$ and $t \neq t'$.
\\ \\
We know $h$ is surjective because the Im $f$ is $S$ and Im $g$ is $T$.
Therefore, for all $t \in T$ there is a solution to $h(r) = t$.
\\ \\
We prove $h(r) + h(r') = h(r + r')$ as such:
\[
h(r) + h(r') = g(f(r)) + g(f(r')) = g(f(r + r')) = h(r + r')
\]
\\
We prove $h(r)h(r') = h(rr')$ as such:
\[
h(r)h(r') = g(f(r))g(f(r')) = g(f(r)f(r')) = g(f(rr')) = h(rr')
\]
Therefore $h$ is an isomorphism and $\cong$ is transitive.

>>>>

\item First, let us prove that $\cong$ is symmetric.
Since $f: R \rightarrow S$ is an isomorphism, this means that $f$ is bijective.
Let $f(r) = s$ for some $r \in R$ and some $s \in S$.
If $f$ is bijective, there exists some function $g: S \rightarrow R$ such that
$g(s) = g(f(r)) = r$. \\ \\
To prove $g$ is injective, let $s, s' \in S$ and $r, r' \in R$ such that
$s \neq s'$, $r \neq r'$, $f(s) = r$, and $f(s') = r'$.  As such,
$g(s) = g(f(r)) = r$ and $g(s') = g(f(r')) = r'$.  Since $r \neq r'$, this
implies that if $s \neq s'$, then $r \neq r'$ and $g$ must be injective. \\ \\
Because Im $f$ = $S$, there is an $r \in R$ for all $s \in S$ such that
$s = f(r)$.  Because $g(s) = g(f(r)) = r$, Im $g$ = $R$ and $g$ is surjective. \\ \\
We can prove that $g(s) + g(s') = g(s + s')$ as such: \\
\[
g(s) + g(s') = g(f(r)) + g(f(r')) = r + r' = g(f(r + r')) = g(f(r) + f(r')) = g(s + s')
\]
\\
We can prove $g(s)g(s') = g(ss')$ as such:
\[
g(s)g(s') = g(f(r))g(f(r')) = rr' = g(f(rr')) = g(f(r)f(r')) = g(ss')
\]
\\
Therefore, $g$ is an isomorphism and $\cong$ is symmetric.
\\ \\
Next, we prove that $\cong$ is transitive.  If $f$ and $g$ are isomorphisms,
then there exists $r \in R$, $s \in S$, and $t \ in T$ such that
$f(r) = s$ and $g(s) = t$.  As such, let $h: R \rightarrow T$ be the function
such that $h(r) = g(f(r)) = g(s) = t$. \\ \\
Let $g(s') = t'$ for some $s' \in S$ and $t' \in T$ such that
$s \neq s'$ and $t \neq t'$.
We know $h$ is injective because $h(r) = g(f(r)) = g(s) = t$ and
$h(r') = g(f(r')) = g(s') = t'$ and $t \neq t'$.
\\ \\
We know $h$ is surjective because the Im $f$ is $S$ and Im $g$ is $T$.
Therefore, for all $t \in T$ there is a solution to $h(r) = t$.
\\ \\
We prove $h(r) + h(r') = h(r + r')$ as such:
\[
h(r) + h(r') = g(f(r)) + g(f(r')) = g(f(r + r')) = h(r + r')
\]
\\
We prove $h(r)h(r') = h(rr')$ as such:
\[
h(r)h(r') = g(f(r))g(f(r')) = g(f(r)f(r')) = g(f(rr')) = h(rr')
\]
Therefore $h$ is an isomorphism and $\cong$ is transitive.

\item Assume $\mathbb{C}$ and $\mathbb{R}$ are isomorphic and
$f: \mathbb{C} \rightarrow \mathbb{R}$.  By the definition of isomorphism,
we know that $f(1) = f(1\cdot1) = f(1)f(1) = f(1)^2$.  If $f(1) = f(1)^2$, then
$f(1)$ must either be 0 or 1.  Assume $f(1) = 0$.  Then, for an $c \in \mathbb{C}$,
$f(c) = f(c\cdot1) = f(c)f(1) = f(c)\cdot0 = 0$, and this is a contradiction since
isomorphisms are bijective.  Therefore, $f(1) = 1$.  Again, by the definition
of isomorphism, $f(-1) = -f(1) = -1$.  Now let $r = f(i)$.  As such,
$r^2 = f(i)f(i) = f(i^1) = f(-1) = -1$.  However, this is a contradiction
because there is no $r \in \mathbb{R}$ such $r^2 = -1$.  Therefore
$\mathbb{C}$ and $\mathbb{R}$ are not isomorphic.
